---
title: Lectures
bibliography: library.bib
biblio-style: apalike
---

```{r, child="_setup.Rmd"}
```

## Introduction to R

### tldr:
>An overview of R, RStudio and github. The focus is on orienting users to R via R Studio and getting comfortable within the IDE.


```{r echo=FALSE, results='asis'}
make_doc_links("introduction")
```

## Good Programming Practices

### tldr:
>Reviewing good programming and data project practices to improve code and reproducibility.

```{r echo=FALSE, results='asis'}
make_doc_links("gpp")
```


## Cleaning Data
### tldr:
>Learn basic data manipulation through the use of the `dplyr` and `tidyr` packages. This includes transforming data between wide and long formats, combining columns and making new calculated columns.

```{r echo=FALSE, results='asis'}
make_doc_links("cleaning")
```

## Dealing with Dates and Times
### tldr:
>Learning how to convert, manipulate, and do calculations on R date time objects through the `lubridate` package.

```{r echo=FALSE, results='asis'}
make_doc_links("datetime")
```

## Factors
### tldr:
>An overivew of how to manipulate categorical data represented in R as "factors" via the `lubridate` package. This includes a brief introduction to modeling in R.

```{r echo=FALSE, results='asis'}
make_doc_links("factors")
```

## Plotting with ggplot2
### tldr:
>An overview of how to create publication quality graphics through the `ggplot2` package. A little discussion of the Grammar of Graphics upon whose philosophies `ggplot2` is built.

```{r echo=FALSE, results='asis'}
make_doc_links("basic_graphing")
```